\LARGE \bf Mean Estimation from One-Bit Measurements

### 2020-12-01 distributed-estimation.tex
Fixed typos. Updated Fig. "optimal density".  Rewrote Conclusions

We now consider consider a restricted case where each detection region is a
half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
against a single threshold. Under adaptive signal acquisition,
this is sufficient for asymptotic optimality;
in non-adaptive settings, it is not sufficient, though we may characterize
a few additional optimality results.
%% As we explain next, the existence of a density
%% for the sequence of thresholds is enough to establish local asymptotic
%% normality and leads to a closed form expression for the precision parameter
%% and the ARE.
Assume now that each $B_i$ is of the form
\begin{equation}
  \label{eq:threshold_message}
  B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
    -1 & X_i > t_i,
  \end{cases}  
\end{equation}
where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder. In
other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and
$\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$. It follows that
\begin{equation}
  L_n(A_1,\ldots,A_n;\theta)
  = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
  \label{eq:Ln_threshold}
\end{equation}
A natural condition for the existence of the limit \eqref{eq:Ln_threshold}
as $n\to \infty$ is that the empirical distribution of the threshold values
converges to a probability measure. Specifically, for an interval $I \subset
\mathbb R$, define
\begin{equation*}
  \lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
\end{equation*}
Then an investigation of the proof of
Theorem~\ref{theorem:non-adaptive-minimax} in
Section~\ref{sec:proof-non-adaptive-minimax}, specifically
Sec.~\ref{sec:proof-lan-bits} and the bounds~\eqref{eqn:h-fourth}, show that
as $\eta(t) \le \eta(0)$ for all $t \in \R$ under
Assumption~\ref{assump:failure_rate}, the following corollary follows. (The
corollary relies on local asymptotic normality~\cite[Ch.~7]{VanDerVaart98};
see Appendix~\ref{sec:proof-sgd-regular} for some brief discussion of such
conditions.)
\begin{cor} \label{cor:LAN_thresh}
  Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that
  $\lambda_n$ converges (weakly) to a probability measure $\lambda$ on
  $\mathbb R$. Then the conclusions of
  Theorem~\ref{theorem:non-adaptive-minimax} apply with
  %% $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a
  %% LAN family with precision parameter
  \begin{equation*}
    \kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
  \end{equation*}
  Moreover, the family of laws of $\{B_i = \sgn(X_i - t_i)\}_{i = 1}^n$
  under $\{P_\theta\}_{\theta \in \Theta}$ is locally asymptotically normal
  with information $\kappa(\theta)$.
\end{cor}

The condition that $\lambda_n$ converges to a probability measure is
satisfied, for example, whenever the $t_1,\ldots,t_n$s are drawn
independently from a probability distribution $\lambda(dt)$ on $\mathbb
R$.

When the conclusions of Corollary~\ref{cor:LAN_thresh} hold, local asymptotic normality of $\{B_n\}_{n=1}^\infty$ implies that the maximum
likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by
${\theta}^{ML}_n$, is local asymptotic minimax in the sense that
\begin{equation*}
  \sqrt{n} \left( {\theta}^{ML}_n - \theta \right)
  \cd \normal\left(0, 1/\kappa(\theta) \right). 
\end{equation*}
We note that ${\theta}^{ML}_n$ solves
\begin{equation}
  \label{eq:ML}
  0 = \sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) }.
\end{equation}
If the collection $\{t_1,t_2\ldots\}$ is bounded
(for example $\{t_1,t_2\ldots\} \subset \Theta$), then
\begin{equation*}
\lim_{n\to \infty} n \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
\end{equation*} 
so that the ML estimator attains the local asymptotic MSE of Theorem~\ref{thm:adpative_lower_bound}.

@@

We conclude this section by considering the density of the threshold values
that maximizes the worst-case information $\inf_\theta \kappa(\theta)
= \kappa_\lambda(\theta)$ where $\kappa_\lambda(\theta)
= \int \eta(t - \theta) d\lambda(t)$.
This distribution $\lambda$ solves the
optimization problem
\begin{align}
  \label{eq:var_cvx_minimax}
  \begin{split}
    \mathrm{maximize} \quad &  \inf_{\theta \in \Theta} \int \eta(t-\theta) \lambda(dt)
    \\ 
    \mathrm{subject~to} 
    \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
  \end{split}
\end{align}
The objective function~\eqref{eq:var_cvx_minimax} is concave in
$\lambda(dt)$ and continuous in the weak topology over measures on $\Theta$,
so that by discretizing, we can approximately solve this problem using
convex optimization. We let $\kappa^\star$ denote the maximal value of
problem~\eqref{eq:var_cvx_minimax} and $\lambda^\star(dt)$ be the density
achieving the maximum. By drawing thresholds
$t_i \simiid \lambda^\star$,
Corollary~\ref{cor:LAN_thresh} guarantees that for any $\theta \in \Theta$, the
maximum likelihood estimator
using $\{B_i = \sgn(X_i - t_i)\}_{i \in \N}$ is at least $\kappa^\star$.
%
%By discretizing the interval $[-b,b]$ using $N_\theta$ values $\theta_1,\ldots,\theta_{N_\theta}$ and the real line using $N_\lambda$ values $\lambda_1,\ldots,\lambda_{N_\lambda}$, the discrete version of \eqref{eq:var_cvx_minimax} is the following linear program (LP) in the variables $K \in \mathbb R$ and $\lambda \in \mathbb R^{N_\lambda}$:
%\begin{align}
%\label{eq:cvx_minimax}
%\begin{split}
%\mathrm{maximize} \quad &  K \\ 
%\mathrm{subject~to} 
%\quad &  K \leq \mathbf H\lambda \\
%& \lambda \geq 0,\quad   \mathbf 1^T\lambda  \leq 1,
%\end{split}
%\end{align}
%where $\mathbf H_{i,j} = \eta(t_i - \theta_j)$, $i=1,\ldots,N_\lambda$, $j = 1,\ldots,N_\theta$. 
%\begin{rem}
%The number of variables in \eqref{eq:cvx_minimax} is $N_\lambda+1$ and number of constraints is $1 + N_\lambda + N_\theta$. Since an LP has an optimal solution at which the number of constraints for which equality holds is no smaller than the number of variables \cite{papadimitriou1998combinatorial}, there exists an optimal $\lambda$ with support over no more than $N_{\theta}$ points. Therefore, in approximating the solution of \eqref{eq:var_cvx_minimax} using 
%\eqref{eq:cvx_minimax}, it is enough to take $N_\lambda = N_\theta$.
%\end{rem}

Figure~\ref{fig:minimax_support} illustrates an approximation to
$\lambda^\star(dt)$ obtained by solving a discretized version of
\eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density
with variance $\sigma^2$ and $\Theta = [-T,T]$. The minimax asymptotic
precision parameter $\kappa^\star$ obtained this way is illustrated in
Fig.~\ref{fig:minimax_ARE} as a function of half the support size $T$. Also
illustrated in these figures is $\kappa_{\unif}$, the precision
parameter corresponding to threshold values uniformly distribution over
$\Theta = [-T,T]$,
\begin{align}
& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
 \\
& = 
\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
\end{align}

\begin{figure}
  %%%%% COMMENTED TIKZ PICTURE %%%%%
  \begin{center}
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
title = {$\sigma/T = 1/2$},
ytick={0,0.1,1},
%ylabel = {$\lambda(dt)$},
yticklabels={0,0.1,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.5.csv};

\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.5.csv};

\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 0.6,
samples=10, 
xlabel= {$dt$},
title = {$\sigma/T = 1/5$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
ytick={0,0.5},
ylabel = {$\lambda(dt)$},
yticklabels={0,0.5},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.2.csv};

\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.2.csv};

\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 0.3,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
title = {$\sigma / T = 1/10$},
xticklabels={-$T$, 0, $T$},
ytick={0,0.2},
%ylabel = {$\lambda(dt)$},
yticklabels={0,0.2},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.1.csv};

\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.1.csv};

\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 0.15,
samples=10, 
xlabel= {$dt$},
title = {$\sigma / T = 1/20$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
ytick={0,0.1},
ylabel = {$\lambda(dt)$},
yticklabels={0,0.1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [x = x, y  = y,col sep=comma] {./Figs/minmax_lmd_b0.5_sig0.05.csv};

\addplot[color = black!30!green, smooth, dashed] plot table [x = x, y  = z,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};

\addplot[color = red, smooth] plot table [x = x, y  = y,col sep=comma] {./Figs/minimax_th_b0.5_sig0.05.csv};

%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}

\caption{\label{fig:minimax_support}
Optimal threshold density $\lambda^\star(dt)$ (blue) that maximizes the ARE for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in [-T,T]$.
%
The continuous curve (red) represents the reciprocal of the asymptotic risk for each $\theta \in [-T,T]$ under the optimal density, i.e., the minimax risk is the inverse of the minimal value of this curve. The dashed curve (green) is the reciprocal of the asymptotic risk for each $\theta \in [-T,T]$ when the threshold values are uniformly distributed over $[-T,T]$, hence its minimal value is the inverse of \eqref{eq:uniform_risk}. }
\end{center}
\end{figure}

\begin{figure}
  %%%%% COMMENTED TIKZ PICTURE %%%%%
  \begin{center}
\begin{tikzpicture}[scale = 1]
\begin{axis}[
width=8cm, height=6cm,
xmax=2.5, 
xmode = log,
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=1, 
xlabel= {$\sigma/T$},
%xtick={-0.5,0,0.5},
%xticklabels={-$$, 0, $b$},
ytick={0,0.637,1},
yticklabels={0,$2/\pi$,1},
ylabel = {$\ARE$},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
\addlegendentry{optimal threshold density};

\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
\addlegendentry{uniform threshold desnity};
\end{axis}
\end{tikzpicture}
\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma/T$ for $f(x) = \Ncal(\theta,\sigma^2)$  and $\theta \in \Theta = [-T,T]$. The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$, where $\kappa_{\unif}$ is given by \eqref{eq:uniform_risk}. }.
\end{center}
\end{figure}

%We have seen that using threshold detection, an ARE $\eta(0)\sigma^2$ can only be attained at a single point in $\Theta$. Next, we prove that with any set of messages obtained via a distributed strategy, there exists at least one $\theta \in \Theta$ such that the estimator of $\theta$ has ARE strictly smaller than $\eta(0)\sigma^2$.

\begin{figure}
\begin{center}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
title = {$\sigma/\sigma_{\theta} = 4$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
ytick={0,1},
ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
title = {$\sigma/\sigma_{\theta} = 3$},
xticklabels={-$T$, 0, $T$},
ytick={0,1},
%ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
title = {$\sigma/\sigma_{\theta} = 2$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
ytick={0,1},
ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
title = {$\sigma/\sigma_{\theta} = 1$},
ytick={0,1},
%ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
\caption{\label{fig:opt_density}
Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=T^2/3$ is the variance of the prior. 
}
\end{center}
\end{figure}

>>>>

We now consider a restricted case where each detection region is a
half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
against a single threshold. Under adaptive signal acquisition,
this is sufficient for asymptotic optimality;
in non-adaptive settings, it is not sufficient, though we may characterize
a few additional optimality results.
%% As we explain next, the existence of a density
%% for the sequence of thresholds is enough to establish local asymptotic
%% normality and leads to a closed form expression for the precision parameter
%% and the ARE.
Assume now that each $B_i$ is of the form
\begin{equation}
  \label{eq:threshold_message}
  B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i<  t_i, \\
    -1 & X_i \geq t_i,
  \end{cases}  
\end{equation}
where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder. In
other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and
$\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$. It follows that
\begin{equation}
  L_n(A_1,\ldots,A_n;\theta)
  = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
  \label{eq:Ln_threshold}
\end{equation}
A natural condition for the existence of the limit \eqref{eq:Ln_threshold}
as $n\to \infty$ is that the empirical distribution of the threshold values
converges to a probability measure. Specifically, for an interval $I \subset
\mathbb R$, define
\begin{equation*}
  \lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
\end{equation*}
Then an investigation of the proof of
Theorem~\ref{theorem:non-adaptive-minimax} in
Section~\ref{sec:proof-non-adaptive-minimax}, specifically
Sec.~\ref{sec:proof-lan-bits} and the bounds~\eqref{eqn:h-fourth}, show that
as $\eta(t) \le \eta(0)$ for all $t \in \R$ under
Assumption~\ref{assump:failure_rate}, the following corollary follows. (The
corollary relies on local asymptotic normality~\cite[Ch.~7]{VanDerVaart98};
see Appendix~\ref{sec:proof-sgd-regular} for some brief discussion of such
conditions.)
\begin{cor} \label{cor:LAN_thresh}
  Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that
  $\lambda_n$ converges (weakly) to a probability measure $\lambda$ on
  $\mathbb R$. Then the conclusions of
  Theorem~\ref{theorem:non-adaptive-minimax} apply with
  %% $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a
  %% LAN family with precision parameter
  \begin{equation*}
    \kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
  \end{equation*}
  Moreover, the family of laws of $\{B_i = \sgn(X_i - t_i)\}_{i = 1}^n$
  under $\{P_\theta\}_{\theta \in \Theta}$ is locally asymptotically normal
  with information $\kappa(\theta)$.
\end{cor}

The condition that $\lambda_n$ converges to a probability measure is
satisfied, for example, whenever $t_1,\ldots,t_n$ are drawn
independently from a probability distribution $\lambda(dt)$ on $\mathbb
R$.

When the conclusions of Corollary~\ref{cor:LAN_thresh} hold, local asymptotic normality of $\{B_n\}_{n=1}^\infty$ implies that the maximum
likelihood estimator (ML) of $\theta$ from $B_1,\ldots,B_n$, denoted here by
${\theta}^{ML}_n$, is local asymptotic minimax in the sense that
\begin{equation*}
  \sqrt{n} \left( {\theta}^{ML}_n - \theta \right)
  \cd \normal\left(0, 1/\kappa(\theta) \right). 
\end{equation*}
We note that ${\theta}^{ML}_n$ solves
\begin{equation}
  \label{eq:ML}
  0 = \sum_{i=1}^n B_i \frac{f \left( t_i-\theta\right) }{F \left(B_i  (t_i-\theta)\right) }.
\end{equation}
If the collection $\{t_1,t_2\ldots\}$ is bounded
(for example $\{t_1,t_2\ldots\} \subset \Theta$), then
\begin{equation*}
\lim_{n\to \infty} n \cdot \ex{\left({\theta}^{ML}_n - \theta \right)^2}  = 1/\kappa(\theta), 
\end{equation*} 
so that the ML estimator attains the local asymptotic MSE of Theorem~\ref{thm:adpative_lower_bound}.

@@

We conclude this section by considering the density of the threshold values
that maximizes the worst-case information $\inf_\theta \kappa(\theta)
= \kappa_\lambda(\theta)$ where $\kappa_\lambda(\theta)
= \int \eta(t - \theta) d\lambda(t)$.
This distribution $\lambda$ solves the
optimization problem
\begin{align}
  \label{eq:var_cvx_minimax}
  \begin{split}
    \mathrm{maximize} \quad &  \inf_{\theta \in \Theta} \int \eta(t-\theta) \lambda(dt)
    \\ 
    \mathrm{subject~to} 
    \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
  \end{split}
\end{align}
The objective function~\eqref{eq:var_cvx_minimax} is concave in
$\lambda(dt)$ and continuous in the weak topology over measures on $\Theta$,
so that by discretizing, we can approximately solve this problem using
convex optimization. We let $\kappa^\star$ denote the maximal value of
problem~\eqref{eq:var_cvx_minimax} and $\lambda^\star(dt)$ be the density
achieving the maximum. By drawing thresholds
$t_i \simiid \lambda^\star$,
Corollary~\ref{cor:LAN_thresh} guarantees that for any $\theta \in \Theta$, the
maximum likelihood estimator
using $\{B_i = \sgn(X_i - t_i)\}_{i \in \N}$ is at least $\kappa^\star$. \par
%
Figure~\ref{fig:minimax_support} illustrates an approximation to
$\lambda^\star(dt)$ obtained by solving a discretized version of
\eqref{eq:var_cvx_minimax} for the case when $f(x)$ is the normal density
with variance $\sigma^2$ and $\Theta = [-1/2,1/2]$. The minimax asymptotic
precision parameter $\kappa^\star$ obtained this way is illustrated in
Fig.~\ref{fig:minimax_ARE} as a function of $\sigma$. Also
illustrated in these figures is $\kappa_{\unif}$, the precision
parameter corresponding to threshold values uniformly distribution over
$\Theta$,
\begin{align}
& \kappa_{\unif} \triangleq \min_{\theta \in [-T,T]} \frac{1}{2T}\int_{-T}^T \eta\left(t-\theta\right) dt \nonumber
 \\
& = 
\frac{1}{2T}\int_{-T}^{T} \eta\left(t\pm T\right) dt
= \frac{1}{2T}\int_{0}^{2T} \eta(t) dt  \label{eq:uniform_risk}. 
\end{align}

\begin{figure}
  %%%%% COMMENTED TIKZ PICTURE %%%%%
  \begin{center}
\input{Figs/opt_thr_den.tex}
\caption{\label{fig:minimax_support}
Optimal threshold density. The threshold density $\lambda^\star(dt)$ (blue) that maximizes the asymptotic relative efficiency for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in [-T,T]$.
%
The continuous curve (red) is the ARE for each $\theta \in [-1/2,1/2]$ under the optimal density, hence the minimax ARE is the minimal value of this curve. The dashed curve (green) is the ARE when the threshold values are uniformly distributed over $[-1/2,1/2]$; its minimal value is $\kappa_{\unif}$ \eqref{eq:uniform_risk}. }
\end{center}
\end{figure}

\begin{figure}
  %%%%% COMMENTED TIKZ PICTURE %%%%%
  \begin{center}
\begin{tikzpicture}[scale = 1]
\begin{axis}[
width=8cm, height=6cm,
xmax=2.5, 
xmode = log,
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=1, 
xlabel= {$\sigma$},
%xtick={-0.5,0,0.5},
%xticklabels={-$$, 0, $b$},
ytick={0,0.637,1},
yticklabels={0,$2/\pi$,1},
ylabel = {\scriptsize Relative Efficiency},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
\addlegendentry{optimal threshold density};

\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
\addlegendentry{uniform threshold desnity};
\end{axis}
\end{tikzpicture}
\caption{\label{fig:minimax_ARE} Minimax ARE versus $\sigma$ for $f(x) = \Ncal(\theta,\sigma^2)$ and $\theta \in \Theta = [-1/2,1/2]$. The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$ of \eqref{eq:uniform_risk}.}.
\end{center}
\end{figure}

%%% Optimal density under a prior %%%%
\iffalse %%% This part have been removed $$$
\begin{figure}
\begin{center}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
title = {$\sigma/\sigma_{\theta} = 4$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
ytick={0,1},
ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig4.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
title = {$\sigma/\sigma_{\theta} = 3$},
xticklabels={-$T$, 0, $T$},
ytick={0,1},
%ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig3.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
title = {$\sigma/\sigma_{\theta} = 2$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
ytick={0,1},
ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig2.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
%
\begin{tikzpicture}[scale = 0.55]
\begin{axis}[
width=8cm, height=6cm,
xmin = -0.5, xmax=0.5, 
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=10, 
xlabel= {$dt$},
xtick={-0.5,0,0.5},
xticklabels={-$T$, 0, $T$},
title = {$\sigma/\sigma_{\theta} = 1$},
ytick={0,1},
%ylabel = {$\lambda(dt)$},
yticklabels={0,1},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = blue, smooth, mark = o ] plot table [col sep=comma] {./Figs/unif_Bayes_lmd_b0.5_sig1.csv};
%\addlegendentry{$\frac{\sigma^2}{\sigma_\theta^2} = 1$};
\end{axis}
\end{tikzpicture}
\caption{\label{fig:opt_density}
Optimal threshold density $\lambda^\star(dt)$ that minimizes the asymptotic Bayes risk \eqref{eq:cvx_average} for a uniform prior with $\sigma/\sigma_\theta=1,2,3,4$, where $\sigma_\theta^2=T^2/3$ is the variance of the prior. 
}
\end{center}
\end{figure}

When a prior $\pi$ on $\Theta$ is provided, one may be interested in the threshold density $\lambda$ minimizing the Bayes risk $R_n(\pi)$. The resulting minimization problem is 
\begin{align}
\label{eq:cvx_average}
\begin{split}
\mathrm{minimize} \quad & R_{\pi} =  \int \frac{\pi(d\theta)}{ \int \eta \left( t-\theta\right) \lambda(dt)}. \\ 
\mathrm{subject~to} \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) =1, 
\end{split}
\end{align}
which is convex in $\lambda$ since $x \rightarrow 1/x$, $x>0$, is convex. Figure~\ref{fig:opt_density}  illustrates the solution to \eqref{eq:cvx_average} for the case of where $f(x)$ is the normal distribution and $\pi$ is the uniform distribution over $\Theta = [-T,T]$. %Figure~\ref{fig:dist_bound_uniform} illustrates the corresponding Bayes risk. 
\fi
